---
title: "Series options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Series options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(uPlot)
```


## Series Colors

To color a serie, use `stroke` argument in `uSeries()`:

```{r series-colors-1}
uPlot(eco2mix[1:50, c("datetime", "wind", "hydraulic")]) %>% 
  uSeries("wind", stroke = "#72cbb7") %>% 
  uSeries("hydraulic", stroke = "#2672b0")
```

Or use `uColors()`:

```{r series-colors-2}
uPlot(eco2mix[1:50, c("datetime", "wind", "hydraulic")]) %>% 
  uColors(
    "wind" = "#72cbb7",
    "hydraulic" = "#2672b0"
  )
```


## Points

Hide points with:

```{r points-hide}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", points = list(show = FALSE))
```

Or customize them with:

```{r points-customize}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries(
    serie = "hydraulic",
    points = list(size = 15, fill = "red", stroke = "blue", width = 3)
  )
```




## Fill colors

Fill in the area underneath the series and customize the alpha value for the filling:

```{r fill-color}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", stroke = "#2672b0", fill = "#2672b0", alpha = 0.5)
```



## Paths

Use `path` argument to modify serie appearance. Default is linear path:

```{r linear-path}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.linear()"))
```

Draw a spline:

```{r spline-path}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.spline()"))
```

Use a function that return `null` to only draw points:

```{r null-path}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("function() {return null;}"))
```


Stepped line with points before:

```{r stepped-path-1}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.stepped({align: 1})"))
```


Stepped line with points after:

```{r stepped-path-2}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.stepped({align: -1})"))
```


Draw bars:

```{r bars-path-1}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.bars()"))
```


Align bars after points and set bars size:

```{r bars-path-2}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", paths = JS("uPlot.paths.bars({align: 1, size: [1]})"))
```


Multiple options in the same time:

```{r}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries(
    serie = "hydraulic", 
    paths = JS("uPlot.paths.bars({align: 1, size: [1]})"),
    stroke = "#FFF", 
    fill = "#2672b0",
    points = list(show = FALSE)
  )
```


## Line stroke and width

Change the width of the line and use a stroke pattern:

```{r}
uPlot(eco2mix[1:50, c("datetime", "hydraulic")]) %>% 
  uSeries("hydraulic", dash = c(5, 5), width = 2)
```

