---
title: "Time formatting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Time formatting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(uPlot)
```

Date-time formats available and R equivalent:

  * YYYY:	%Y, e.g. 2025
  * YY: %y, e.g. 25
  * MMMM:	%B, e.g. July
  * MMM: %b, e.g. Jul
  * MM:	%m, e.g. 07
  * M: ?, e.g. 7
  * DD: %d, e.g. 09
  * D: %e, e.g. 9,
  * WWWW:	%A, e.g. Monday
  * WWW: %a, e.g. Mon
  * HH: %H, e.g. 03
  * H: ?, e.g. 3  (unpadded)
  * h: %I , e.g. 9 (12hr, unpadded)
  * AA:	%P , e.g. AM
  * aa:	%p , e.g. am
  * mm: %m , e.g. 08
  * m: ? , e.g. 8 (unpadded)
  * ss: %s , e.g. 04
  * s: ? , e.g. 4 (unpadded)
  * fff:	milliseconds, 374



## Format date-time globally

Use the same format in legend and axes : 

```{r fmt-global}
uPlot(
  data = eco2mix[1:150, c(1, 2, 6)],
  options = list(
    fmtDate = htmlwidgets::JS("tpl => uPlot.fmtDate('{DD}/{MM}\\n{H}h');")
  )
)
```

Change months and days labels : 

```{r months-names}
uPlot(
  data = temperatures[1:150, c(1, 2)],
  options = list(
    fmtDate = htmlwidgets::JS(
      sprintf(
        "tpl => uPlot.fmtDate('{WWW} {DD}\\n{MMMM}', %s);",
        jsonlite::toJSON(list(
          MMMM = c("janvier", "février", "mars", "avril", "mai", "juin", "juillet", "août", "septembre", "octobre", "novembre", "décembre"),
          MMM = c("jan","fév","mar","avr","mai","juin","juil","août","sept","oct","nov", "déc"),
          WWWW = c("dimanche", "lundi", "mardi", "mercredi", "jeudi", "vendredi", "samedi"),
          WWW = c("dim","lun","mar","mer","jeu","ven","sam")
        ))
      )
    )
  )
)
```



## Format legend

Specify format to use in date-time serie options :

```{r fmt-legend}
uPlot(eco2mix[1:150, c(1, 2, 6)]) %>%
  uSeries(
    serie = "datetime", # column name
    value = "{DD}/{MM}/{YYYY} at {H}h"
  )
```


## Format y axis

Always use same format for axis ticks : 

```{r y-axis-same}
uPlot(eco2mix[1:950, c(1, 2, 6)]) %>%
  uAxesX(
    values = "{DD}/{MM} {H}h"
  )
```


Specify a custom array to highlight breakpoints and deal with different levels of zoom : 

```{r y-axis-custom}
eco2mix %>% 
  subset(format(datetime, "%Y") == "2020", select = c(1, 2, 6)) %>% 
  uPlot(use_gzipped_json = TRUE) %>%
  uAxesX(
    values = list(
      #    tick incr        Default        year                         month day                     hour  min           sec   mode
      list(3600 * 24 * 365, "{YYYY}",      NULL,                        NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600 * 24 * 28,  "{MMM}",       "\n{YYYY}",                  NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600 * 24,       "{MM}/{DD}",   "\n{YYYY}",                  NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600,            "{H}h",        "\n{MM}/{DD}/{YY}",          NULL, "\n{MM}/{DD}",          NULL, NULL,         NULL, 1),
      list(60,              "{H}:{mm}",    "\n{MM}/{DD}/{YY}",          NULL, "\n{MM}/{DD}",          NULL, NULL,         NULL, 1),
      list(1,               ":{ss}",       "\n{MM}/{DD}/{YY} {H}:{mm}", NULL, "\n{MM}/{DD} {H}:{mm}", NULL, "\n{H}:{mm}", NULL, 1),
      list(0.001,           ":{ss}.{fff}", "\n{MM}/{DD}/{YY} {H}:{mm}", NULL, "\n{MM}/{DD} {H}:{mm}", NULL, "\n{H}:{mm}", NULL, 1)
    )
  )
```


Custom month names combined with axis formatting:

```{r y-axis-months}
eco2mix %>% 
  subset(format(datetime, "%Y") == "2020", select = c(1, 2, 6)) %>% 
  uPlot(
    use_gzipped_json = TRUE,
    options = list(
      fmtDate = htmlwidgets::JS(
        sprintf(
          "tpl => uPlot.fmtDate(tpl, %s);",
          jsonlite::toJSON(list(
            MMMM = c("janvier", "février", "mars", "avril", "mai", "juin", "juillet", "août", "septembre", "octobre", "novembre", "décembre"),
            MMM = c("jan","fév","mar","avr","mai","juin","juil","août","sept","oct","nov", "déc"),
            WWWW = c("dimanche", "lundi", "mardi", "mercredi", "jeudi", "vendredi", "samedi"),
            WWW = c("dim","lun","mar","mer","jeu","ven","sam")
          ))
        )
      )
    )
  ) %>%
  uAxesX(
    values = list(
      #    tick incr        Default        year                         month day                     hour  min           sec   mode
      list(3600 * 24 * 365, "{YYYY}",      NULL,                        NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600 * 24 * 28,  "{MMM}",       "\n{YYYY}",                  NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600 * 24,       "{MM}/{DD}",   "\n{YYYY}",                  NULL, NULL,                   NULL, NULL,         NULL, 1),
      list(3600,            "{H}h",        "\n{MM}/{DD}/{YY}",          NULL, "\n{MM}/{DD}",          NULL, NULL,         NULL, 1),
      list(60,              "{H}:{mm}",    "\n{MM}/{DD}/{YY}",          NULL, "\n{MM}/{DD}",          NULL, NULL,         NULL, 1),
      list(1,               ":{ss}",       "\n{MM}/{DD}/{YY} {H}:{mm}", NULL, "\n{MM}/{DD} {H}:{mm}", NULL, "\n{H}:{mm}", NULL, 1),
      list(0.001,           ":{ss}.{fff}", "\n{MM}/{DD}/{YY} {H}:{mm}", NULL, "\n{MM}/{DD} {H}:{mm}", NULL, "\n{H}:{mm}", NULL, 1)
    )
  )
```

Note that in `uPlot.fmtDate`, first argument is `tpl` which is default formatting.



See https://github.com/leeoniya/uPlot/tree/master/docs for more documentation.

